Associations between chlorophyll *a* and various microcystin-LR health advisory

### 2016-01-17 manuscript/manuscript.Rmd
working on f1000 format

---
title: Associations between chlorophyll *a* and various microcystin-LR health advisory
  Concentrations
author:
- affilnum: 1
  email: hollister.jeff@epa.gov
  name: Jeffrey W. Hollister
- affilnum: 1
  name: Betty J. Kreakie
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    template: components/f1000research.latex
  html_document: null
capsize: normalsize
csl: components/ecology.csl
documentclass: article
fontsize: 11pt
linenumbers: yes
bibliography: components/manuscript.bib
spacing: doublespacing
abstract: no
---

>>>>

---
title: Associations between chlorophyll *a* and various microcystin-LR health advisory
  Concentrations
author:
- affilnum: 1
  email: hollister.jeff@epa.gov
  name: Jeffrey W. Hollister
- affilnum: 1
  name: Betty J. Kreakie
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    template: components/f1000research.latex
  html_document: null
capsize: normalsize
csl: components/plos.csl
documentclass: article
fontsize: 11pt
linenumbers: yes
bibliography: components/manuscript.bib
spacing: doublespacing
abstract: no
---
